\chapter*{Preface}
This work is the culmination of many months of hard work, with many opportunities to learn and experience. Over the past year I have been fortunate enough to get acquainted with humanitarian aid processes and the role geographic information has within it. These insights have been an inspiration for this research and allowed me to put the Master's degree Geomatics for the Built Environment in context of real world applications. At the conclusion of this Master's programme, I can say that I have found my personal drivers and my little place from where I can contribute to a better world. \\

\noindent The process of research and study however, is a path of cooperation, support and learning from others. I would like to thank those who have inspired and supported me throughout. First of all I would to thank my two mentors guiding the thesis process. Jorge and Stef, thank you very much for the all the feedback in the various meetings we had every two weeks. The ideas and concepts you were able to elaborate to me guided me through the process and allowed me to gain purpose in the research. Thank you for steering me back to the main topic on moments my ideas where to broad for a Master's thesis, and explaining that others would be able to start their research from the questions I left unanswered. Besides my main mentors I would like to thank Luc Willekens and Agung Indrajit for their feedback in the official process; and Sisi Zlatanova for her inspiring work on Geomatics for disasters and commencing support for the project.\\

\noindent Secondly, thank you very much to the 510 team from the Netherlands Red Cross. The work done with regards to information within humanitarian aid is an inspiration to me. A special thanks to Stefania for the support of the project and for reading all materials I made for this thesis. Furthermore I was considerably helped by Andy Thean, his expertise and technical understanding allowed me to interpret existing methods and apply those on new datasets.\\

\noindent I would also like to thank my co-student from the Geomatics program. Thank you all very much for the great two years with many experiences. Unfortunately we saw each other less often in the last year but we had so much fun, and shared so much of the stress. And Wicked Climbers, we will climb some more!\\

\noindent Lastly I would like to thank my family. Sorry parents, for moving back in after my Bachelor's. However, I am very grateful as it allowed me to focus on my studies and research. Nicoline, thank you for listening to all the information I had regarding my thesis, even if it was boring, unstructured, or just plain incomprehensible. Thank you all very much for all the support and guidance throughout the process. 